Machine Learning, Building Vintage and Property Values

### 2019-09-04 text/manuscript_assa.Rmd
Small text changes, abstract

---
title: "Machine Learning, Building Vintage and Property Values"
author: "Thies Lindenthal* (University of Cambridge) & Erik B. Johnson (University of Alabama)"
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: Externalities of architecture, machine learning
fig_caption: yes
header-includes:
   - \usepackage{soul}
   - \usepackage{color}
   - \sethlcolor{yellow}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{graphicx}
   - \usepackage{grffile}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{setspace}
   - \usepackage{multirow}
   - \doublespacing
   - \usepackage[backend=bibtex, style=authoryear]{biblatex}
fig_width: 6
fig_height: 4
output: 
  pdf_document:
    keep_tex: true
bibliography: references.bib
abstract: "This paper first introduces an algorithm that collects pictures of individual buildings from Google Street View. Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of building vintages. Third, it investigates whether architectural styles influence house prices. For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings. Additionally, through the comparison of expert classification and deep learning methods, we are able to illustrate some of the limitations of machine learning methods and provide guidance on how to detect and overcome these limitations." 
---

>>>>

---
title: "Machine Learning, Building Vintage and Property Values"
author: "Thies Lindenthal* (University of Cambridge) & Erik B. Johnson (University of Alabama)"
date: "`r format(Sys.time(), '%d %B %Y')`"
tags: Externalities of architecture, machine learning
fig_caption: yes
header-includes:
   - \usepackage{soul}
   - \usepackage{color}
   - \sethlcolor{yellow}
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{graphicx}
   - \usepackage{grffile}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{setspace}
   - \usepackage{multirow}
   - \doublespacing
   - \usepackage[backend=bibtex, style=authoryear]{biblatex}
fig_width: 6
fig_height: 4
output: 
  pdf_document:
    keep_tex: true
bibliography: references.bib
abstract: "This paper first introduces an algorithm that collects pictures of individual buildings from Google Street View. Second, it trains a deep convolutional neural network (CNN) to classify residential buildings into architectural styles, taking into account spatial dependencies of building vintages. Third, it investigates whether architectural styles influence house prices. For re-sales, the architectural style is a significant determinant of transaction prices while no such effect is found for new buildings. Additionally, we are able to provide guidance on how to detect and overcome some of the limitations of machine learning methods through a large-scale comparison of predictions and expert classifications." 
---

### 2019-09-04 text/manuscript_assa.tex
Small text changes, abstract

\begin{document}
\maketitle
\begin{abstract}
This paper first introduces an algorithm that collects pictures of
individual buildings from Google Street View. Second, it trains a deep
convolutional neural network (CNN) to classify residential buildings
into architectural styles, taking into account spatial dependencies of
building vintages. Third, it investigates whether architectural styles
influence house prices. For re-sales, the architectural style is a
significant determinant of transaction prices while no such effect is
found for new buildings. Additionally, through the comparison of expert
classification and deep learning methods, we are able to illustrate some
of the limitations of machine learning methods and provide guidance on
how to detect and overcome these limitations.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
This paper first introduces an algorithm that collects pictures of
individual buildings from Google Street View. Second, it trains a deep
convolutional neural network (CNN) to classify residential buildings
into architectural styles, taking into account spatial dependencies of
building vintages. Third, it investigates whether architectural styles
influence house prices. For re-sales, the architectural style is a
significant determinant of transaction prices while no such effect is
found for new buildings. Additionally, we are able to provide guidance
on how to detect and overcome some of the limitations of machine
learning methods through a large-scale comparison of predictions and
expert classifications.
\end{abstract}
